\begin{abstract}
Singular value decomposition (SVD) has many useful applications in various fields, 
while current implementations are still time-consuming, especially when matrix size becomes to ten thousands of order of magnitude.
Modern General Purpose GPUs have shown their extreme computational advantages in parallel computing.
In our paper, we present an implementation of one effective bidiagonal SVD method, bisection and twisted algorithm, with CUDA programming on Nvidia GPU.
The algorithm can calculate all singular values and vectors at the time cost of $O(n^2)$ in serial.
Additionally, It is able to obtain any subsets of singular values and vectors directly.
This feature is suitable for current applications that does not require the whole SVD calculation.
We design our GPU kernels carefully.
It only takes 0.8 second to obtain all the singular values and vectors with single procision on GeForce 750Ti when matrix size is $10k*10k$, and 1.3 seconds on Tesla K40c with double precision.
It is up to $10$ times faster than MKL divide-and-conquer routine DBDSDC with $8$ cores $16$ threads,
and $36$ times faster than CULA QR routine DBDSQR on the same GPU.
Our results also show that our algorithm has better performance than previous SVD approaches on CPU and GPU. 
We also evaluate the effect of execution time when different number of block is allocated, and analyze the performance when error tolerance becomes strict.
In addition, we improve our implementation to a huge matrix size with 1 million $\times$ 1 million.
To our knowledge, No implementation has achieved such size.
\end{abstract}

\begin{IEEEkeywords}
Singular Valu Decomposition; GPU; Twisted fraction; Bisection algorithm.

\end{IEEEkeywords}
